### 2022-08-10 doc/src/IMSIC.tex
Guest interrupt files do not support value 0x40000000 for eidelivery

When the hypervisor extension is implemented and a device is being
managed directly by a guest operating system, MSI addresses from the
device are initially guest physical addresses, as they are configured
at the device by the guest OS.
These guest addresses must be translated by an I/O MMU, which gets
configured by the hypervisor to redirect those MSIs to the interrupt
files for the correct guest external interrupts.
For more on this topic, see Chapter~\ref{ch:IOMMU}.

@@

>>>>

When the hypervisor extension is implemented and a device is being
managed directly by a guest operating system, MSI addresses from the
device are initially guest physical addresses, as they are configured
at the device by the guest OS.
These guest addresses must be translated by an \mbox{IOMMU}, which gets
configured by the hypervisor to redirect those MSIs to the interrupt
files for the correct guest external interrupts.
For more on this topic, see Chapter~\ref{ch:IOMMU}.

@@

Guest interrupt files do not support
value \z{0x40000000} for \z{eidelivery}.
